---
title: "Pilot test"
---

Pilot study
```{r, echo=FALSE}
setwd("/Users/hycho/Documents/14FALL-Research/201503 AUC simulation/AUCCI_GJM")
sim212 <- readRDS("simdata_212.rds")
sim311 <- readRDS("simdata_311.rds")
sim1111 <- readRDS("simdata_1111.rds")
```

**1. complete data**

$\theta=0.9$, $\phi=0.5$, $n=100$, n.sim=10,000
```{r, echo=FALSE}
sim212$eval
```

$\theta=0.95$, $\phi=0.5$, $n=200$, n.sim=10,000
```{r, echo=FALSE}
sim311$eval
```

**Analysis (assuming normality)**

A. CM (Wald) has poor CP

B. Mee and RG have nice CP, and they have balanced NCP's.

C. NS1 & 2 almost always have inflated CP.


<br>
<br>

**2. incomplete data**

$\theta=0.8$, $\phi=0.5$, $n=200$, $\rho=0.25$, n.sim=2,000, m=10, R=30

(ignore 4.imp.norm)
```{r, echo=FALSE}
sim1111
```

**Analysis (assuming normality)**

A. Direct approaches usually have CP around 92 ~ 93%, while MI approach varies along with methodsfrom 89 ~ 94%

B. The average CI lengths are stable for MI approaches (around 0.13), while it varies a lot for Direct approaches (between 0.13 ~ 0.17)
